Power analysis of MRR studies

### 2022-06-22 writeUp/power_analysis_only_hawaii.tex
added final submission

%   \doublespacing
% \raggedright
\title{A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Figures}
\author{Ben Lambert, Ace North, Charles Godfray}

\begin{document}
\maketitle

\section{Lifespan estimates}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l}
		\textbf{Analysis} & \textbf{Grouping} & \textbf{Log-likelihood} & \textbf{z} & \textbf{p}\\
		\hline
		MRR & genus & -7315.2 & - & -\\
		& overall & -7511.0 & 11.3 & 0.0\\
		& species & -7748.9 & 5.5 & 0.0\\
		\hline
		Detinova & species & -14,672.4 & - & -\\
		& species-complex & -15,504.9 & 3.6 & 0.0\\
		& continent & -16,731.1 & 0.4 & 0.3\\
		\hline
		Polovodova & species & -3818.3 & - & -\\
		& genus & -3848.3 & 0.4 & 0.3\\
		& overall & -3895.5 & 0.4 & 0.4\\
	\end{tabular}
		\caption{\textbf{Model comparison by K-fold cross-validation.} Here, we present the estimates of model fit on hold-out datasets (see SOM) as measured by the sum of the pointwise log-likelihood values averaged across all posterior draws (in the ``Log-likelihood'' column) across each of the three analyses and each grouping of studies considered. Within each row-block (``MRR'', ``Detinova'', ``Polovodova''), the models are arranged according to the point estimate of the fit: best at top; worst at bottom. The $z$ scores show the scaled difference in the averaged pointwise log-likelihood \citep{vehtari2015efficient} versus the model immediately above it in the ranking, and the ``p'' column shows the corresponding $p$ values representing the cumulative density function from a standard normal.}
\end{table}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Aedes} & \textit{simpsoni s.l.} & 6.3 & 11.3 & 18.3 & 31.8 & 75.0 & 26.9 & 29.5 \\
		\textit{Aedes} & \textit{communis} & 10.0 & 13.2 & 15.4 & 18.2 & 24.3 & 16.2 & 5.2 \\
		\textit{Anopheles} & \textit{koliensis} & 6.7 & 10.5 & 15.2 & 24.0 & 56.5 & 21.9 & 25.2 \\
		\textit{Anopheles} & \textit{punctulatus} & 7.2 & 10.7 & 15.1 & 22.8 & 48.9 & 20.3 & 28.6 \\
		\textit{Aedes} & \textit{cantans} & 9.7 & 12.0 & 13.9 & 16.1 & 20.6 & 14.4 & 4.7 \\
		\textit{Aedes} & \textit{albopictus} & 8.0 & 10.0 & 11.6 & 13.7 & 17.7 & 12.1 & 3.4 \\
		\textit{Anopheles} & \textit{albimanus} & 5.9 & 8.6 & 11.6 & 16.9 & 35.7 & 15.2 & 18.7 \\
		\textit{Anopheles} & \textit{darlingi} & 4.9 & 7.3 & 10.2 & 16.0 & 37.5 & 14.5 & 14.8 \\
		\textit{Anopheles} & \textit{maculatus} & 5.7 & 7.9 & 10.2 & 13.7 & 24.3 & 12.2 & 8.7 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 4.6 & 7.3 & 9.1 & 11.4 & 18.2 & 10.1 & 6.9 \\
		\textit{Anopheles} & \textit{sergenti} & 3.6 & 5.9 & 8.7 & 13.8 & 32.6 & 12.4 & 13.4 \\
		\textit{Aedes} & \textit{triseriatus} & 5.6 & 6.6 & 7.5 & 8.5 & 10.7 & 7.7 & 1.8 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 4.2 & 5.4 & 6.4 & 7.7 & 10.5 & 6.8 & 2.1 \\
		\textit{Aedes} & \textit{africanus} & 3.4 & 5.1 & 6.2 & 7.8 & 11.9 & 7.0 & 9.3 \\
		\textit{Aedes} & \textit{aegypti} & 2.8 & 4.5 & 6.2 & 8.5 & 13.9 & 7.0 & 3.8 \\
		\textit{Culex} & \textit{quinquefasciatus} & 4.3 & 5.2 & 5.9 & 7.0 & 9.4 & 6.3 & 1.8 \\
		\textit{Culex} & \textit{nigripalpus} & 3.5 & 4.6 & 5.8 & 7.5 & 11.3 & 6.4 & 3.1 \\
		\textit{Aedes} & \textit{notoscriptus} & 2.9 & 4.0 & 5.4 & 8.2 & 20.2 & 7.9 & 9.5 \\
		\textit{Culex} & \textit{pipiens} & 3.4 & 4.4 & 5.2 & 6.4 & 9.0 & 5.6 & 2.0 \\
		\textit{Anopheles} & \textit{saperoi} & 3.5 & 4.2 & 4.9 & 5.8 & 8.2 & 5.2 & 2.0 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 3.0 & 3.8 & 4.4 & 5.1 & 6.4 & 4.5 & 1.1 \\
		\textit{Aedes} & \textit{melanimon} & 3.3 & 3.9 & 4.3 & 4.8 & 5.7 & 4.4 & 1.0 \\
		\textit{Anopheles} & \textit{funestus s.l.} & 2.9 & 3.6 & 4.2 & 4.8 & 6.0 & 4.3 & 1.0 \\
		\textit{Anopheles} & \textit{lesteri} & 2.4 & 3.2 & 3.9 & 5.0 & 7.5 & 4.4 & 2.1 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 3.3 & 3.6 & 3.9 & 4.2 & 4.8 & 4.0 & 0.5 \\
		\textit{Anopheles} & \textit{pseudopunctipennis s.l.} & 2.3 & 2.9 & 3.5 & 4.3 & 6.7 & 3.8 & 1.9 \\
		\textit{Aedes} & \textit{vexans} & 1.9 & 2.3 & 2.6 & 3.0 & 4.1 & 2.8 & 1.0 \\
		\textit{Culex} & \textit{tarsalis} & 1.9 & 2.1 & 2.3 & 2.4 & 2.7 & 2.3 & 0.3 \\
		\textit{Anopheles} & \textit{vestitipennis} & 1.3 & 1.8 & 2.2 & 2.9 & 4.4 & 2.5 & 1.2 \\
		\textit{Anopheles} & \textit{albitarsis s.l.} & 1.3 & 1.6 & 1.9 & 2.2 & 2.9 & 2.0 & 1.0 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.7 & 0.9 & 1.1 & 1.2 & 1.6 & 1.1 & 1.0 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 0.4 & 0.6 & 0.8 & 1.1 & 2.4 & 1.1 & 2.6 \\
		\hline
		\textit{Aedes} & \text{} & 2.8 & 4.8 & 6.9 & 10.0 & 17.2 & 8.1 & 4.9 \\
		\textit{Anopheles} & \text{} & 1.5 & 3.0 & 5.0 & 8.4 & 17.8 & 6.8 & 6.4 \\
		\textit{Culex} & \text{} & 1.1 & 1.8 & 2.5 & 3.5 & 5.6 & 2.9 & 1.5 \\
		\hline
		\textbf{Overall} & \text{} & 1.4 & 2.8 & 4.6 & 7.5 & 15.4 & 6.0 & 5.2 \\
	\end{tabular}
	\caption{\textbf{MRR: mean unfed female mosquito lifespan estimates.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan. Units of lifespan are days.}
	\label{tab:mrr_estimated_lifespans}%
\end{table}%

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_female_blood_sugar_inkscaped.pdf}}
	\caption{\textbf{MRR: female mosquito mean lifespan by pre-release feeding status.} Labels to the left of the vertical axis indicate genus or overall grouping; the labels to the right of the axis indicate pre-release feeding status. The middle line in each box shows the median estimates and the solid point indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:mrr_female_blood_sugar}
\end{figure}

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/mrr_lifeSpanVsRange.pdf}}
	\caption{\textbf{MRR: mean mosquito lifespan versus trapping range.} The markers show the median posterior lifespan estimates for each time series with the lower and upper bounds indicating the 25\% and 75\% quantiles, respectively. The black line shows a linear regression line estimated using the median posterior lifetimes, with the grey shading indicating 95\% confidence intervals. All estimates were obtained using the non-hierarchical exponential survival model.}
	\label{fig:mrr_lifeSpanVsRange}
\end{figure}

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/detinova_insecticide.pdf}}
	\caption{\textbf{Detinova dissection: estimated impact of insecticide on lifespan.} The middle line in each box shows the median estimates. The left and right box whiskers show the 10\%, and 90\% posterior quantiles respectively.}
	\label{fig:detinova_insecticide}
\end{figure}

\begin{figure}[h]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/detinova_individual_lifespan_no_insecticide.pdf}}
	\caption{\textbf{Detinova dissection: individual time-series estimates of adult mosquito mean lifespan.} The middle line in each box shows the median estimates. The left and right box whiskers show the 25\%, and 75\% posterior quantiles respectively. Note, that a handful of observations are not shown in the plot since their estimates exceeded the reasonable range (here deemed to be up to 12 cycles).}
	\label{fig:detinova_lifespan_individual}
\end{figure}

\begin{table}[htbp!]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} &
		\textbf{75$\%$} & \textbf{95$\%$} & \textbf{Mean} & \textbf{Std. dev.} \\
		\hline
		\textit{Anopheles} & \textit{gambiae (Form M)} & 0.9 & 1.8 & 2.6 & 3.6 & 6.7 & 3.2 & 4.6 \\
		\textit{Anopheles} & \textit{gambiae} & 0.6 & 1.1 & 1.7 & 2.7 & 5.6 & 2.2 & 2.2 \\
		\textit{Anopheles} & \textit{arabiensis} & 0.4 & 0.9 & 1.5 & 2.6 & 6.3 & 2.3 & 3.9 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.7 & 3.1 & 6.3 & 21.2 & 7.3 & 56.1 \\
		\textit{Anopheles} & \textit{moucheti} & 1.0 & 1.9 & 2.8 & 4.2 & 8.9 & 3.8 & 6.3 \\
		\textit{Anopheles} & \textit{funestus} & 0.8 & 1.6 & 2.7 & 4.4 & 10.6 & 4.0 & 10.6 \\
		\textit{Anopheles} & \textit{funestus s.l.} & 0.6 & 1.2 & 2.1 & 3.7 & 9.8 & 3.3 & 4.8 \\
		\textit{Anopheles} & \textit{nili s.l.} & 1.0 & 1.4 & 1.7 & 2.1 & 2.8 & 1.8 & 0.6 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 0.9 & 1.5 & 2.1 & 2.8 & 4.8 & 2.4 & 1.8 \\
		\textit{Anopheles} & \textit{dirus (formerly Sp. A)} & 0.5 & 1.0 & 1.5 & 2.2 & 4.2 & 1.8 &
		1.5 \\
		\textit{Anopheles} & \textit{dirus s.l.} & 0.6 & 1.2 & 2.0 & 3.1 & 7.4 & 2.9 & 6.8 \\
		\textit{Anopheles} & \textit{aconitus} & 0.5 & 1.1 & 1.8 & 2.8 & 6.3 & 2.5 & 4.7 \\
		\textit{Anopheles} & \textit{sundaicus s.l.} & 0.4 & 0.9 & 1.6 & 2.9 & 7.5 & 2.7 & 7.4 \\
		\textit{Anopheles} & \textit{minimus s.l.} & 0.5 & 1.1 & 1.6 & 2.5 & 5.8 & 2.3 & 5.6 \\
		\textit{Anopheles} & \textit{fluviatilis s.l.} & 0.4 & 0.9 & 1.4 & 2.3 & 5.1 & 2.0 & 3.0 \\
		\textit{Anopheles} & \textit{maculatus s.l.} & 0.6 & 1.0 & 1.2 & 1.6 & 2.5 & 1.4 & 0.8 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 0.3 & 0.7 & 1.2 & 2.0 & 4.9 & 1.8 & 2.3 \\
		\textit{Anopheles} & \textit{annularis s.l.} & 0.3 & 0.7 & 1.2 & 2.0 & 4.7 & 1.7 & 1.9 \\
		\textit{Anopheles} & \textit{sinensis} & 0.4 & 0.8 & 1.1 & 1.7 & 3.0 & 1.4 & 1.0 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 0.5 & 0.8 & 1.1 & 1.5 & 2.3 & 1.2 & 0.6 \\
		\textit{Anopheles} & \textit{anthropophagus (lesteri)} & 0.4 & 0.9 & 1.4 & 2.3 & 5.1 & 2.0 &
		3.0 \\
		\textit{Anopheles} & \textit{lesteri s.l.} & 0.3 & 0.6 & 1.1 & 1.9 & 4.7 & 1.7 & 2.4 \\
		\textit{Anopheles} & \textit{barbirostris s.l.} & 0.4 & 0.7 & 1.0 & 1.4 & 2.8 & 1.2 & 1.3 \\
		\textit{Anopheles} & \textit{albitarsis (formerly Sp C)} & 0.8 & 2.0 & 3.9 & 8.4 &
		32.6 & 13.3 & \text{$>$100} \\
		\textit{Anopheles} & \textit{albitarsis (formerly Sp A)} & 0.2 & 0.4 & 0.6 & 1.0 & 2.3 & 0.8
		& 0.9 \\
		\textit{Anopheles} & \textit{albitarsis (Sp. B)} & 0.1 & 0.3 & 0.6 & 0.9 & 1.9 & 0.7 & 0.8
		\\
		\textit{Anopheles} & \textit{albitarsis s.l.} & 0.4 & 0.9 & 1.5 & 3.0 & 8.3 & 2.8 & 5.8 \\
		\textit{Anopheles} & \textit{nuneztovari s.l.} & 0.3 & 0.6 & 1.1 & 1.9 & 4.4 & 1.6 & 2.3 \\
		\textit{Anopheles} & \textit{darlingi} & 0.2 & 0.7 & 1.2 & 2.4 & 6.7 & 2.2 & 4.2 \\
		\textit{Anopheles} & \textit{albimanus} & 0.2 & 0.5 & 0.9 & 1.6 & 3.6 & 1.3 & 1.6 \\
		\textit{Anopheles} & \textit{aquasalis} & 0.3 & 0.6 & 1.1 & 1.8 & 4.4 & 1.6 & 4.0 \\
		\textit{Anopheles} & \textit{aquasalis s.l.} & 0.2 & 0.4 & 0.7 & 1.0 & 2.4 & 0.9 & 1.3 \\
	\end{tabular}
	\caption{\textbf{Detinova dissection: mean female mosquito lifespan estimates in terms of gonotrophic cycles.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
	\label{tab:detinova_lifespan_gonotrophic}%
\end{table}

\begin{table}[htbp]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Anopheles} & \textit{sergentii} & 1.0 & 1.9 & 2.5 & 3.4 & 6.2 & 3.0 & 2.5 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.2 & 1.9 & 2.9 & 5.4 & 2.4 & 1.9 \\
		\textit{Culex} & \textit{thalassius} & 1.1 & 1.6 & 1.8 & 2.1 & 2.9 & 1.9 & 1.0 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.5 & 1.6 & 1.7 & 1.7 & 1.9 & 1.7 & 0.1 \\
		\textit{Anopheles} & \textit{minimus} & 0.7 & 1.2 & 1.7 & 2.2 & 4.1 & 2.0 & 2.2 \\
		\textit{Anopheles} & \textit{maculipennis} & 0.8 & 1.1 & 1.4 & 1.8 & 2.9 & 1.6 & 0.7 \\
		\textit{Culex} & \textit{pipiens} & 1.1 & 1.3 & 1.4 & 1.5 & 1.7 & 1.4 & 0.2 \\
		\textit{Mansonia} & \textit{uniformis} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{rivulorum} & 0.8 & 1.0 & 1.1 & 1.1 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{melas} & 0.8 & 1.0 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{culicifacies} & 0.9 & 1.0 & 1.0 & 1.1 & 1.2 & 1.0 & 0.1 \\
		\textit{Anopheles} & \textit{subpictus} & 0.6 & 0.9 & 1.0 & 1.2 & 2.1 & 1.2 & 2.0 \\
		\textit{Aedes} & \textit{aegypti} & 0.5 & 0.8 & 1.0 & 1.2 & 2.0 & 1.2 & 3.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 0.7 & 0.9 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{stephensi} & 0.6 & 0.8 & 1.0 & 1.1 & 1.6 & 1.0 & 0.4 \\
		\textit{Anopheles} & \textit{darlingi} & 0.7 & 0.8 & 0.9 & 1.0 & 1.3 & 1.0 & 0.2 \\
		\textit{Culex} & \textit{quinquefasciatus} & 0.4 & 0.7 & 0.9 & 1.3 & 2.2 & 1.1 & 0.6 \\
		\textit{Aedes} & \textit{polynesiensis} & 0.8 & 0.9 & 0.9 & 0.9 & 1.0 & 0.9 & 0.1 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.3 & 0.6 & 0.9 & 1.3 & 4.2 & 2.5 & 30.8 \\
		\textit{Culex} & \textit{annulirostris} & 0.5 & 0.8 & 0.9 & 1.0 & 1.4 & 0.9 & 0.5 \\
		\textit{Aedes} & \textit{samoanus} & 0.6 & 0.7 & 0.8 & 0.9 & 1.0 & 0.8 & 0.2 \\
		\textit{Aedes} & \textit{sollicitans} & 0.4 & 0.5 & 0.6 & 0.8 & 1.3 & 0.7 & 0.5 \\
		\textit{Aedes} & \textit{vexans} & 0.4 & 0.5 & 0.6 & 0.7 & 0.9 & 0.6 & 0.7 \\
		\textit{Anopheles} & \textit{cruzii} & 0.3 & 0.5 & 0.5 & 0.7 & 1.1 & 0.6 & 0.4 \\
		\textit{Anopheles} & \textit{bellator} & 0.3 & 0.4 & 0.5 & 0.6 & 1.0 & 0.6 & 1.8 \\
		\hline
		\textit{Anopheles} & \textit{} & 0.6 & 1.0 & 1.4 & 1.9 & 3.2 & 1.6 & 0.9 \\
		\textit{Mansonia} & \textit{} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Culex} & \textit{} & 0.5 & 0.8 & 1.0 & 1.4 & 2.3 & 1.2 & 0.6 \\
		\textit{Aedes} & \textit{} & 0.6 & 0.7 & 0.8 & 0.9 & 1.1 & 0.8 & 0.2 \\
		\hline
		\textbf{Overall} & \textit{} & 0.5 & 0.8 & 1.2 & 1.7 & 2.7 & 1.3 & 0.7 \\
	\end{tabular}
	\caption{\textbf{Polovodova dissection: mean female mosquito lifespan in terms of gonotrophic cycles.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
	\label{tab:dissection_estimated_lifespans}%
\end{table}

\begin{table}[htbp!]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} &
		\textbf{75$\%$} & \textbf{95$\%$} & \textbf{Mean} & \textbf{Std. dev.} \\
		\hline
		\textit{Anopheles} & \textit{gambiae (Form M)} & 3.3 & 6.2 & 8.7 & 11.9 & 22.3 & 10.7 & 14.9
		\\
		\textit{Anopheles} & \textit{gambiae} & 2.0 & 3.8 & 5.8 & 9.0 & 18.4 & 7.6 & 7.1 \\
		\textit{Anopheles} & \textit{arabiensis} & 1.4 & 3.2 & 5.3 & 8.8 & 20.8 & 7.7 & 11.9 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 2.5 & 5.7 & 10.3 & 20.6 & 68.4 & 23.9 &
		\text{$>$100} \\
		\textit{Anopheles} & \textit{moucheti} & 3.5 & 6.4 & 9.2 & 13.9 & 29.0 & 12.5 & 19.7 \\
		\textit{Anopheles} & \textit{funestus} & 2.9 & 5.7 & 9.0 & 14.5 & 34.4 & 13.4 & 31.0 \\
		\textit{Anopheles} & \textit{funestus s.l.} & 2.0 & 4.3 & 7.1 & 12.5 & 32.2 & 11.1 & 15.6 \\
		\textit{Anopheles} & \textit{nili s.l.} & 3.6 & 4.8 & 5.8 & 7.1 & 9.6 & 6.1 & 2.0 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 3.4 & 5.3 & 7.1 & 9.5 & 16.2 & 8.2 & 6.2 \\
		\textit{Anopheles} & \textit{dirus (formerly Sp. A)} & 1.9 & 3.6 & 5.1 & 7.4 & 13.8 & 6.2 &
		5.0 \\
		\textit{Anopheles} & \textit{dirus s.l.} & 2.0 & 4.4 & 6.8 & 10.5 & 24.1 & 9.8 & 23.0 \\
		\textit{Anopheles} & \textit{aconitus} & 1.9 & 4.0 & 6.2 & 9.6 & 20.7 & 8.5 & 15.4 \\
		\textit{Anopheles} & \textit{sundaicus s.l.} & 1.5 & 3.4 & 5.6 & 9.7 & 24.7 & 9.1 & 23.6 \\
		\textit{Anopheles} & \textit{minimus s.l.} & 1.9 & 3.8 & 5.5 & 8.3 & 19.2 & 7.9 & 17.8 \\
		\textit{Anopheles} & \textit{fluviatilis s.l.} & 1.6 & 3.2 & 5.0 & 7.8 & 16.9 & 6.8 & 9.6 \\
		\textit{Anopheles} & \textit{maculatus s.l.} & 2.2 & 3.5 & 4.5 & 5.6 & 8.6 & 4.9 & 2.6 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.2 & 2.6 & 4.3 & 6.9 & 16.0 & 6.1 & 7.5 \\
		\textit{Anopheles} & \textit{annularis s.l.} & 1.1 & 2.5 & 4.3 & 6.9 & 15.6 & 5.8 & 6.2 \\
		\textit{Anopheles} & \textit{sinensis} & 1.6 & 2.8 & 4.1 & 5.9 & 10.3 & 4.8 & 3.2 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 1.9 & 3.0 & 4.0 & 5.2 & 8.0 & 4.3 & 2.0 \\
		\textit{Anopheles} & \textit{anthropophagus (lesteri)} & 1.6 & 3.2 & 5.0 & 7.7 & 16.9 & 6.8
		& 9.9 \\
		\textit{Anopheles} & \textit{lesteri s.l.} & 0.9 & 2.2 & 3.9 & 6.5 & 15.6 & 5.7 & 7.8 \\
		\textit{Anopheles} & \textit{barbirostris s.l.} & 1.4 & 2.5 & 3.5 & 4.9 & 9.6 & 4.3 & 4.1 \\
		\textit{Anopheles} & \textit{albitarsis (formerly Sp C)} & 3.0 & 6.8 & 13.0 & 27.3
		& \text{$>$100} & 44.2 & \text{$>$100} \\
		\textit{Anopheles} & \textit{albitarsis (formerly Sp A)} & 0.6 & 1.3 & 2.2 & 3.7 & 7.7 & 3.0
		& 3.1 \\
		\textit{Anopheles} & \textit{albitarsis (Sp. B)} & 0.5 & 1.2 & 2.0 & 3.3 & 6.6 & 2.6 & 2.6
		\\
		\textit{Anopheles} & \textit{albitarsis s.l.} & 1.2 & 3.1 & 5.4 & 9.9 & 26.9 & 9.3 & 18.6 \\
		\textit{Anopheles} & \textit{nuneztovari s.l.} & 1.0 & 2.3 & 3.9 & 6.4 & 14.7 & 5.6 & 7.6 \\
		\textit{Anopheles} & \textit{darlingi} & 0.9 & 2.4 & 4.5 & 8.1 & 22.0 & 7.4 & 13.6 \\
		\textit{Anopheles} & \textit{albimanus} & 0.9 & 2.0 & 3.3 & 5.4 & 12.0 & 4.5 & 5.3 \\
		\textit{Anopheles} & \textit{aquasalis} & 1.0 & 2.3 & 3.9 & 6.3 & 14.4 & 5.6 & 12.9 \\
		\textit{Anopheles} & \textit{aquasalis s.l.} & 0.8 & 1.6 & 2.4 & 3.8 & 8.2 & 3.3 & 4.1 \\
	\end{tabular}
	\caption{\textbf{Detinova dissection: mean female mosquito lifespan estimates in terms of chronological time.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.  Units of lifespan are days.}
	\label{tab:detinova_lifespan_chronological}%
\end{table}

\begin{table}[htbp!]
	\begin{tabular}{l|l|l|l|l|l|l|l|l}
		\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Culex} & \textit{thalassius} & 5.7 & 8.2 & 9.4 & 11.0 & 15.6 & 10.1 & 5.2 \\
		\textit{Anopheles} & \textit{sergentii} & 3.7 & 6.4 & 8.5 & 11.5 & 20.6 & 10.1 & 8.1 \\
		\textit{Culex} & \textit{pipiens} & 5.7 & 6.6 & 7.2 & 7.8 & 8.9 & 7.2 & 1.0 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 2.4 & 4.3 & 6.4 & 9.8 & 18.3 & 8.0 & 6.3 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 4.8 & 5.5 & 5.9 & 6.3 & 6.9 & 5.9 & 0.6 \\
		\textit{Anopheles} & \textit{minimus} & 2.7 & 4.4 & 5.8 & 7.7 & 13.7 & 6.9 & 8.1 \\
		\textit{Anopheles} & \textit{maculipennis} & 2.8 & 4.0 & 5.1 & 6.4 & 9.6 & 5.5 & 2.3 \\
		\textit{Culex} & \textit{quinquefasciatus} & 2.0 & 3.4 & 4.8 & 6.9 & 11.7 & 5.6 & 3.3 \\
		\textit{Aedes} & \textit{aegypti} & 2.3 & 3.7 & 4.7 & 5.6 & 9.3 & 5.6 & 12.3 \\
		\textit{Culex} & \textit{annulirostris} & 2.7 & 3.9 & 4.6 & 5.4 & 7.5 & 4.9 & 2.4 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 1.6 & 3.2 & 4.6 & 7.2 & 22.8 & 13.0 & 174.0 \\
		\textit{Mansonia} & \textit{uniformis} & 3.4 & 4.0 & 4.4 & 4.9 & 5.5 & 4.5 & 0.7 \\
		\textit{Aedes} & \textit{polynesiensis} & 3.2 & 3.7 & 4.1 & 4.5 & 5.1 & 4.1 & 0.6 \\
		\textit{Anopheles} & \textit{rivulorum} & 2.8 & 3.4 & 3.8 & 4.2 & 5.0 & 3.9 & 0.7 \\
		\textit{Anopheles} & \textit{melas} & 2.8 & 3.3 & 3.7 & 4.1 & 4.8 & 3.8 & 0.7 \\
		\textit{Anopheles} & \textit{culicifacies s.l.} & 2.8 & 3.3 & 3.7 & 4.1 & 4.7 & 3.7 & 0.6 \\
		\textit{Anopheles} & \textit{subpictus s.l.} & 2.2 & 3.1 & 3.7 & 4.5 & 7.0 & 4.3 & 6.6 \\
		\textit{Aedes} & \textit{samoanus} & 2.7 & 3.2 & 3.6 & 4.0 & 4.9 & 3.7 & 1.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 2.4 & 3.1 & 3.5 & 4.0 & 4.8 & 3.6 & 0.8 \\
		\textit{Anopheles} & \textit{stephensi} & 2.1 & 2.9 & 3.5 & 4.2 & 5.7 & 3.7 & 1.5 \\
		\textit{Anopheles} & \textit{darlingi} & 2.3 & 2.9 & 3.4 & 3.8 & 4.7 & 3.4 & 0.9 \\
		\textit{Aedes} & \textit{sollicitans} & 1.6 & 2.3 & 2.9 & 3.6 & 6.1 & 3.3 & 2.5 \\
		\textit{Aedes} & \textit{vexans} & 1.7 & 2.2 & 2.7 & 3.1 & 4.2 & 3.0 & 3.3 \\
		\textit{Anopheles} & \textit{cruzii} & 1.2 & 1.6 & 2.0 & 2.5 & 4.0 & 2.2 & 1.3 \\
		\textit{Anopheles} & \textit{bellator} & 1.0 & 1.4 & 1.7 & 2.1 & 3.6 & 2.1 & 5.4 \\
		\hline
		\textit{Culex} & \textit{} & 2.5 & 4.0 & 5.4 & 7.6 & 12.3 & 6.2 & 3.2 \\
		\textit{Anopheles} & \textit{} & 2.1 & 3.6 & 4.9 & 6.8 & 10.8 & 5.5 & 2.9 \\
		\textit{Mansonia} & \textit{} & 3.3 & 4.0 & 4.5 & 4.9 & 5.6 & 4.5 & 0.8 \\
		\textit{Aedes} & \textit{} & 2.5 & 3.3 & 3.8 & 4.3 & 5.2 & 3.8 & 0.9 \\
		\hline
		\textit{Overall} & \textit{} & 2.0 & 3.3 & 4.7 & 6.4 & 10.2 & 5.2 & 2.6 \\
	\end{tabular}
	\caption{\textbf{Polovodova dissection: mean female mosquito lifespan estimates in terms of chronological time.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan. Units of lifespan are days.}
	\label{tab:dissection_estimated_lifespans_chron}%
\end{table}

\section{Evidence for senescence}

\begin{figure}[ht]
	\centerline{\includegraphics[width=1.25\textwidth]{./Figure_files/elpd_vs_exponential_ordered_dissection.png}}
	\caption{\textbf{Polovodova dissection: evidence for senescence.}  Here, we consider the predictive accuracy of age-dependent models of mortality versus the exponential model by species. The predictive accuracy was determined using K-Fold cross-validation as described in SOM; the measure of accuracy presented here by the central dots is the difference in estimated expected log pointwise predictive density compared to the exponential model. The lower and upper whiskers represent the lower and upper bounds of the 95\% confidence interval in predictive accuracy. The species have been ordered so that those with the highest average predictive accuracy across all age-dependent models compared to the exponential model appear at the top. If all age-dependent models outperform the exponential, we deem this as evidence for age-dependent mortality (`+'); if a subsample of models perform better, we deem the evidence ambiguous (`?'); and if no age-dependent model exceeds the performance of the exponential, we conclude no evidence in favour of senescence (`-').}
	\label{fig:dissection_senescence}
\end{figure}

>>>>

%   \doublespacing
% \raggedright
\title{Power analysis of MRR studies}
\author{Ben Lambert}

\begin{document}
